\large Multi-Robot Probabilistic Mapping and Exploration

### 2018-06-09 Dissertation/Proposal/DissertationProposalEvanKaufmanNov16.tex
gitignore & dissertation updated

\setbeamertemplate{footline}%{split theme}
{%
  \leavevmode%
  \hbox{\begin{beamercolorbox}[wd=.9\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm plus1fill]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.1\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm plus1fill]{title in head/foot}
    \usebeamerfont{title in head/foot}\mypaper\hfill \insertframenumber/\inserttotalframenumber
  \end{beamercolorbox}}%
  \vskip0pt%
} \setbeamercolor{box}{fg=black,bg=yellow}

\title[Autonomous Exploration by Expected Information Gain from Prob. Occupancy Grid Mapping]
{\large Autonomous Exploration by Expected Information Gain from Probabilistic Occupancy Grid Mapping}

@@

\institute{\footnotesize
{\normalsize Evan Kaufman, Taeyoung Lee, and Zhuming Ai}\vspace*{0.2cm}\\
  Mechanical and Aerospace Engineering\\ George Washington University \vspace*{0.6cm}\\ {\normalsize Special Thanks to Ira. S. Moskowitz and Mark Livingston} \vspace*{0.2cm}\\Information Management \& Decision Architectures\\U.S. Naval Research Laboratory}

@@

\section*{}
\subsection*{Background and Motivation}

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Building Maps and Exploration
	\begin{itemize}
		\item Search and rescue: quickly building a map and finding targets in places with physical or health hazards
		\item Surveillance: gather information of enemy locations
    		\item Convenience: autonomous robotic cleaning
	\end{itemize}
	\pause
	\item Goals
	\begin{itemize}
		\item Build \emph{accurate} probabilistic maps
		\item Use map properties to \emph{predict} how the \emph{map information} will change with various actions
		\item Motion planning for \emph{collision-free} trajectories
		\item Generate algorithms capable of \emph{real-time} implementation
	\end{itemize}
\end{itemize}

\only<1->{
\begin{figure}
\centerline{
    \includegraphics[height=2.1cm]{ogm_ex3.jpeg}\hspace*{0.1cm}
\hspace*{0.5cm}
    \includegraphics[height=2.1cm]{ogm_ex1.jpg}\hspace*{0.1cm}
\hspace*{0.5cm}
    \includegraphics[height=2.1cm]{ogm_ex2.png}\hspace*{0.1cm}
}
\end{figure}}
\end{frame}

\begin{frame}
\frametitle{Background: Occupancy Grid Mapping}
	\begin{itemize}
		\item Environment decomposed into evenly-space grid cells
		\item \emph{Binary} random variable: cells are either \emph{occupied} or \emph{free}
		\item Sensor reading $z$, the \emph{forward sensor model} is $p(z|m,X)$ is the measurement probability density, assuming the stochastic properties are known
		\begin{figure}[!htbp]
		\vspace*{-0.0cm}
		%\vspace*{0.25cm}
		\centerline{
	  	  \includegraphics[width=7cm]{BeamModel.png}\hspace*{0.1cm}
	    	}
		\vspace*{0.25cm}
		\centerline{
	    	\includegraphics[width=5cm]{1D_True_Grid.png}\hspace*{0.1cm}
		%    \hspace*{0.75cm}
	    	}
		{Beam Model for Range Finders}
	\end{figure}
	    	\item Goal: generate a \emph{probabilistic} map $m$ given robot pose $X$
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Background: Occupancy Grid Mapping}
	\begin{itemize}
		\item Cell occupancy probabilities obtained using the \emph{inverse sensor model}, $P(m|z,X)$, which gives grid cell probabilities based on the latest measurement $z$
		\item The exact inverse sensor model was believed to require $\mathcal O(2^n)$ for \emph{each} grid cell within the sensor field of view, so popular substitutes were \emph{heuristic} or \emph{learned} solutions
		\item Recently, the exact inverse sensor model was solved in real-time by grouping map outcomes
		\begin{figure}[!htbp]
		\vspace*{0.5cm}
		\centerline{
			\includegraphics[width=4.0cm]{rkplus_1.png}\hspace*{-0.5cm}
			\includegraphics[width=4.0cm]{rkplus_2.png}}
		 \centerline{
		\includegraphics[width=4.0cm]{rkplus_3.png}\hspace*{-0.5cm}
		\includegraphics[width=4.0cm]{rkplus_4.png}}
		\end{figure}
		\item By grouping, the inverse sensor model requires $\mathcal O(n+1)$, compared with $\mathcal O(2^n)$: applied in \emph{real-time}
	\end{itemize}
\end{frame}

% check here
%\begin{frame}
%\frametitle{Exact Occupancy Grid Mapping: Hallway Comparison}
%	\begin{itemize}
%		\item Comparison between approximate and exact results
%		\begin{figure}[!htbp]
%		    \centering
%		    \begin{subfigure}{.45\textwidth}
%		        \centering
%		        \includegraphics[width=\textwidth]{map_comparison.png}
%		        \caption*{Occupancy Grid Map}
%		    \end{subfigure}
%		    \hspace*{-.05\textwidth}
%		    \begin{subfigure}{.45\textwidth}
%		        \centering
%		        \includegraphics[width=\textwidth]{map_zoom.png}
%		        \caption*{Zoomed In Map}
%		    \end{subfigure}
%		\end{figure}
%	\end{itemize}
%\end{frame}

\begin{frame}
\frametitle{Exact Occupancy Grid Mapping: Hallway Comparison}
\begin{minipage}[t]{0.4\textwidth}
\begin{itemize}
	\item Occupancy grid mapping using an approximate and the exact solution are compared
	\item Both algorithms subject to the same pose and measurement sets 
	\item The exact algorithm yields a more \emph{certain} map shown with entropy $H$ (blue: certain, red: uncertain)
\end{itemize}
\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
		\begin{figure}[!htbp]
		    \centering
		    \begin{subfigure}{0.5\textwidth}
		        \centering
		        \includegraphics[width=.8\textwidth]{AISM_Image_19.pdf}
		        \caption*{Approx. $P(m)$}
		    \end{subfigure}
		    \hspace*{-0.1\textwidth}
		    \begin{subfigure}{0.5\textwidth}
		        \centering
		        \includegraphics[width=.8\textwidth]{EISM_Image_19.pdf}
		        \caption*{Exact $P(m)$}
		    \end{subfigure}
		\end{figure}
		\vspace*{-.1\textwidth}
		\begin{figure}[!htbp]
		    \centering
		    \begin{subfigure}{0.5\textwidth}
		        \centering
		        \includegraphics[width=.8\textwidth]{AISM_Image_inf_19.pdf}
		        \caption*{Approx. $H$}
		    \end{subfigure}
		    \hspace*{-0.1\textwidth}
		    \begin{subfigure}{0.5\textwidth}
		        \centering
		        \includegraphics[width=.8\textwidth]{EISM_Image_inf_19.pdf}
		        \caption*{Exact $H$}
		    \end{subfigure}
		\end{figure}
	\end{minipage}

%	\begin{itemize}
%		\item The exact algorithm yields a more \emph{certain} map from the same measurement set
%		\begin{figure}[!htbp]
%		    \centering
%		    \begin{subfigure}{0.5\textwidth}
%		        \centering
%		        \includegraphics[width=.5\textwidth]{AISM_Image_inf_19.pdf}
%		        \caption*{Approximate}
%		    \end{subfigure}
%		    \hspace*{-0.1\textwidth}
%		    \begin{subfigure}{0.5\textwidth}
%		        \centering
%		        \includegraphics[width=0.5\textwidth]{EISM_Image_inf_19.pdf}
%		        \caption*{Exact}
%		    \end{subfigure}
%		\end{figure}
%	\end{itemize}
\end{frame}

\section*{}
\subsection*{Autonomous Exploration}

\begin{frame}
\frametitle{Autonomous Exploration Description}
\begin{itemize}
        \item The environment is initially unknown, so the robot path is initially uncertain
	\item Simultaneous localization and mapping assumes robotic actions are provided
	\item Human interaction is common to guide the robot
	\item Goal: develop effective policies to govern robotic motion that generates a map accurately and efficiently
\end{itemize}

@@

\begin{frame}
\frametitle{Background: Autonomous Exploration}
\begin{itemize}
        	\item Uncertainty-Based Exploration
	\begin{itemize}
		\item Main idea: choose robot motions that minimize the uncertainty of the occupancy grid map
		\item Equivalently maximize map information gain
	\end{itemize}
\end{itemize}
\begin{minipage}[t]{7.0cm}
\begin{itemize}
	\item Entropy
	\begin{itemize}		
		\item \emph{Shannon's entropy} serves as an uncertainty measure
		\begin{align*}
			H(P)=-P\log P-\bar{P}\log \bar{P}%-(1-P)\log(1-P)
		\end{align*}
		with cell occupancy probability $P$ and complement $\bar{P}=1-P$
		\item Entropy $H$ is maximized when $P=0.5$ and minimized as $P\rightarrow0$ or $P\rightarrow1$
	\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[t]{3.0cm}
\vspace*{0.5cm}
\begin{figure}[!htbp]
	\centerline{
		\hspace*{1.25cm}
   		\includegraphics[width=5.0cm]{H_Plotted_square.pdf}%\hspace*{0.1cm}
	}
\end{figure}
\end{minipage}

@@

\begin{frame}
\frametitle{Related Work}
\begin{itemize}
        	\item Frontier-Based Exploration
	\begin{itemize}
		\item Main idea: robot moves toward boundaries between certain and uncertain space, takes measurements, then pushes back the boundaries
		\item Typically not based directly on grid cell entropy
		\item Heuristic
	\end{itemize}
	\pause
	\item Entropy-Based Exploration
	\begin{itemize}
		\item Cell occupancy probabilities are inaccurate: inverse sensor model is heuristic or learned, and frequently estimated with Rao-Blackwellized particle filters
		\item Inaccurate probabilities imply inaccurate entropy measures
		\item Approaches use ``hallucination measurements'' to predict how future measurements \emph{might} affect the map uncertainty,
		\begin{align*}
			\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right]\approx H(P(m|X_{1:t},Z_{1:t},X_c,\text{E}\left[Z_c\right]))
		\end{align*}
	\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Direct Entropy Calculation}
\begin{itemize}
        \item Instead of relying on frontiers or making assumptions about measurements, the expected map entropy is \emph{calculated directly} by the expected value:
	\begin{align*}
		\text{E}[H(P(m|X,z))]=\int_{z_\text{min}}^{z_\text{max}}
		H(P(m|X,z))p(z|X)dz,
	\end{align*}
	\pause
	\item The integral is discretized by intersections between the measurement and grid cells:
	\begin{align*}
		\text{E}[H(P(m|X,z))]=\sum_{k=1}^{n+1}\bigg\{H(P(m|X,z_k))P(z_{k}|X)\bigg\}
	\end{align*}
	\pause
	\item Entropy $H(P(m|X,z_k))$ is obtained with the exact inverse sensor model and definition of entropy
	\item Probability $P(z_{k}|X)$ is obtained with normalizing values from the exact inverse sensor model
\end{itemize}

\begin{frame}
\frametitle{Direct Entropy Calculation: Computational Challenges}
\begin{itemize}
        \item Problem: $\text{E}[H(P(m|X,z))]$ requires $\mathcal O((n+1)^2)$ for $n+1$ possible measurement outcomes: measurement detects any of the $n$ cells or returns a maximum reading
        \pause
        \item Solution: select the $\hat n$ most probable outcomes for $\mathcal O(\hat n^2)$
        \pause
        \item Monte Carlo simulations ($100$ trials) to determine the expected entropy of a measurement ray compare the exact and approximate resulting accuracies and times
\end{itemize}

		\begin{figure}[!htbp]
		    \centering
		    \begin{subfigure}{0.5\textwidth}
		        \centering
		        \includegraphics[width=.8\textwidth]{simpar_approx_err.pdf}
		        \caption*{Error}
		    \end{subfigure}
		    \hspace*{-0.1\textwidth}
		    \begin{subfigure}{0.5\textwidth}
		        \centering
		        \includegraphics[width=.8\textwidth]{simpar_approx_t.pdf}
		        \caption*{Time Ratio}
		    \end{subfigure}
		\end{figure}

\begin{frame}
\frametitle{Pose Selection}

\begin{minipage}[t]{7.0cm}
\begin{itemize}
	\item Several locations serve as candidates for the robot to move toward
	\item The optimal attitude at each location maximized expected information gain
	\item The pose (location and attitude) with the largest overall expected information gain is selected
	\item Other costs, such as distance or travel time, can be included in the optimization
\end{itemize}
\end{minipage}
\begin{minipage}[t]{3.0cm}
\vspace*{0.5cm}
\begin{figure}[!htbp]
	\centerline{
		\hspace*{1.0cm}
   		\includegraphics[width=5.0cm]{pose_selection}%\hspace*{0.1cm}
	}
\end{figure}
\end{minipage}

\begin{frame}
\frametitle{Collision-Free Path}

\begin{itemize}
	\item \emph{Waypoints}
	\begin{itemize}
		\item Using the grid map as the graph, \emph{Dijkstra's algorithm} provides collision-free waypoints for the robot path
		\item Probability of collision at pose $X$ must be within threshold $\beta>0$,
		\begin{align*}
			P_\text{collision}(X)=1-\prod_{i\in\mathcal C_X}P(\bar{\mathbf{m}}_i|X_{1:t},Z_{1:t})\leq\beta
		\end{align*}
	\end{itemize}
	\pause
	\item \emph{Constrained Polynomial Least Squares}
	\begin{itemize}
		\item Smooth trajectory as a function of time minimizes the squared error between the curve and the waypoints
		\item Constrained to beginning and terminal poses
		\item For complicated trajectories, splines are patched together by constraining position and velocity at the connection
	\end{itemize}
\end{itemize}

@@

%% VIDEO 1: Simulation %%
\begin{frame}
%\href{run:JIRS16_simulation_speedup10x_then_speedup100x.mov}{Simulation Video Link}
\frametitle{Numerical Results}
	\centering{
	\includemovie[poster,autoplay]{\textwidth}{0.66667\textwidth}{JIRS16_simulation_speedup10x_then_speedup100x.mov}}
\end{frame}

@@

%% VIDEO 2: Experiment %%
\begin{frame}
%\href{run:JIRS16_experiment_SideBySide_speedup8x.mov}{Experimental Video Link}
\frametitle{Experimental Results}
	\centering{
	\includemovie[poster,autoplay]{\textwidth}{0.5625\textwidth}{JIRS16_experiment_SideBySide_speedup8x.mov}}
\end{frame}

>>>>

\setbeamertemplate{footline}%{split theme}
{%
  \leavevmode%
  \hbox{\begin{beamercolorbox}[wd=.7\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm plus1fill]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm]{title in head/foot}
    \usebeamerfont{title in head/foot}\mypaper\hfill \insertframenumber/\inserttotalframenumber
    \usebeamerfont{title in head/foot}\hfill \insertframenumber/\inserttotalframenumber
  \end{beamercolorbox}}%
  \vskip0pt%
} \setbeamercolor{box}{fg=black,bg=yellow}

\title[Multi-Robot Probabilistic Mapping and Exploration]{\large Multi-Robot Probabilistic Mapping and Exploration}

@@

\institute{\footnotesize
{\normalsize Evan Kaufman\\Research Advisor: Taeyoung Lee}\vspace*{0.2cm}\\
  Mechanical and Aerospace Engineering\\ George Washington University \vspace*{0.6cm}\\ {\normalsize Special Thanks to Zhuming Ai, \\Ira. S. Moskowitz, and Mark Livingston} \vspace*{0.2cm}\\Information Management \& Decision Architectures\\U.S. Naval Research Laboratory}

@@

\section*{}
\subsection*{Research Description}

\begin{frame}
\frametitle{Intelligent Microflyer}
\begin{itemize}
	\item Description and Motivations
	\begin{itemize}
    		\item Description: determine a method for multiple flying vehicles to autonomously explore an uncertain space while generating a map
		\item Surveillance or search-and-rescue
		\item Particularly useful for potentially dangerous environments
%		\item Research problems within these goals are approached with several unrealistic assumptions or computational limitations
		\item Collaborative effort with the NRL and GWU, focussing on localization, \emph{mapping}, and \emph{autonomous exploration}
	\end{itemize}
	\pause
	\item Goals
	\begin{itemize}
		\item Determine \emph{accurate} probabilistic maps
    		\item Avoid inexact solutions using heuristic or learned solutions
		\item Consider map attributes explicitly to determine an exploration strategy
		\item Use \emph{map expectations} to plan multiple vehicle paths simultaneously
		\item Generate algorithms capable of \emph{real-time} implementation
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{itemize}
	\item Probabilistic Mapping
	\begin{itemize}
    		\item Exact solution to a probabilistic map
		\item Computationally-efficient solution for real-time implementation
	\end{itemize}
	\item Single-Robot Autonomous Exploration
	\begin{itemize}
    		\item Entropy-based solution relies on map uncertainty
		\item Direct computationally-efficient solution
	\end{itemize}
	\item Future Direction: Multi-Robot Autonomous Exploration
	\begin{itemize}
		\item Centralized mapping from several measurement sources
		\item Robots assigned actions from a bidding-based approach
	\end{itemize}
\end{itemize}
\end{frame}

\section*{}

\begin{frame}
\frametitle{}
%\center
\center{\bf \color{blue} Probabilistic Mapping}
\end{frame}

\subsection*{Probabilistic Mapping}
\begin{frame}
\frametitle{Background}

\begin{itemize}
    \item Robotic Mapping
    \begin{itemize}
    	\item Goal: generate a map representing surrounding regions
	\item Crucial for simultaneous localization and mapping (SLAM) and autonomous exploration of uncertain environments
    	\item Popular mapping representations include \emph{occupancy grids}, octomaps, and feature-based maps
    \end{itemize}
\item Occupancy Grid Mapping
\begin{itemize}
	\item The environment may be decomposed into evenly spaced grid cells that are either \emph{occupied} or \emph{free}
	\item Probabilistic map: the goal is to obtain the \emph{probability} of each grid cell being occupied
\end{itemize}
\end{itemize}

\only<1->{
\begin{figure}
\centerline{
    \includegraphics[height=2.1cm]{ogm_ex3.jpeg}\hspace*{0.1cm}
\hspace*{0.5cm}
    \includegraphics[height=2.1cm]{ogm_ex1.jpg}\hspace*{0.1cm}
\hspace*{0.5cm}
    \includegraphics[height=2.1cm]{ogm_ex2.png}\hspace*{0.1cm}
}
\end{figure}}

@@

\begin{frame}
\frametitle{Problem Definition}

\begin{itemize}
	\item The Map and the Robot
	\begin{itemize}
	\item Map $m$ is composed of $n_m$ grid cells with known location and size
	\item The $i$-th grid cell $\mathbf{m}_i$ is a \emph{static binary} random variable, independent of other grid cells: $P(m)=P(\mathbf{m}_1,\mathbf{m}_2,\ldots,\mathbf{m}_{n_m})=\prod_{i=1}^{n_m}P(\mathbf{m}_i)$
	\item \emph{Pose $X_t$} is known, containing robot \emph{position} and \emph{attitude}
	\end{itemize}
\vspace*{0.0cm}\pause
\end{itemize}
\begin{minipage}[t]{7.0cm}
\begin{itemize}
	\item Depth Measurements
	\begin{itemize}
	\item Each measurement origin and direction is known \emph{deterministically}
	\item A measurement \emph{scan} $Z_t=\braces{z_{t,1},z_{t,2},\ldots,z_{t,n_z}}$ contains $n_z$ measurement \emph{rays} (depths)% at the $t$-th time step, and the history of measurement scans $Z_{1:t}$ is known
\item The \emph{forward sensor model} is known from the sensor properties
\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[t]{3.0cm}
%The \emph{forward sensor model} is the probability density distribution $p(z_{t,l}|m,X_{t})$  known from the sensor properties
\hspace*{0.25cm}
\begin{figure}[!htbp]
\vspace*{-0.25cm}
%\vspace*{0.25cm}
\centerline{
    \includegraphics[width=3.5cm]{BeamModel.png}\hspace*{0.1cm}
    }
\vspace*{0.25cm}
\centerline{
    \includegraphics[width=2.5cm]{1D_True_Grid.png}\hspace*{0.1cm}
%    \hspace*{0.75cm}
    }
{Beam Model for Range Finders}
\end{figure}

\end{minipage}

\begin{frame}
\frametitle{Problem Definition}

\begin{itemize}
	\item Bayesian Framework
	\begin{itemize}
	\item Markov Assumption: latest a priori cell occupancy probabilities capture the information from all prior observations
	\item Log-Odds Ratio: popular representation due to simple additive update structure and probability truncation avoidance, but requires the \emph{assumption}
	\begin{align*}
		P(Z_t|\mathbf{m}_i,X_{1:t},Z_{1:t-1})\approx P(Z_t|\mathbf{m}_i,X_t)
	\end{align*}
	\end{itemize}
\vspace*{0.0cm}\pause
	\item Inverse Sensor Model
	\begin{align*}
P(\mathbf{m}_i|z_{t,l},&X_{1:t},Z_{1:t-1})\nonumber
\\
&=\eta_{t,l} \textcolor{blue}{\sum_{m\in\mathcal{M}_i}}p(z_{t,l}|m,X_{t})P(m|X_{1:t-1},Z_{1:t-1}).
\end{align*}
	\begin{itemize}
	\item Given $n$ grid cells: $\textcolor{blue}{\mathcal O(2^n)}$ is \emph{computationally intractable}, motivating a different solution
	\end{itemize}
\end{itemize}

\begin{frame}
\frametitle{Related Work }

\begin{minipage}[t]{7.0cm}
\begin{itemize}
	\item Approximate a function for the inverse sensor model based on intuition
	\begin{itemize}
		\item Simple to implement, but mathematically inaccurate
	\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[t]{3.0cm}
\begin{figure}[!htbp]
\centerline{
    \vspace*{-0.5cm}
%	\hspace*{0.25cm}
    \includegraphics[width=4.0cm]{Approx_ISM_shortened.png}\hspace*{0.1cm}
    }
\centerline{
    \includegraphics[width=3.5cm]{1D_True_Grid.png}
%    \hspace*{0.75cm}
    }
		\end{figure}
\end{minipage}
\vspace*{-0.5cm}
\begin{itemize}
	\item Find a solution through learning
	\begin{itemize}
		\item Simulate maps, poses, and measurements and use learning to obtain an inverse sensor model
		\item Complicated, unclear how these parameters are chosen
	\end{itemize}
	\item Goal: design a \emph{simple} and \emph{accurate} occupancy grid mapping method avoiding log-odds ratio assumptions
\end{itemize}

\begin{frame}
\frametitle{Single Measurement Ray}

\begin{itemize}
    \item Main idea: make use of occupancy grid mapping \emph{assumptions} and extract \emph{patterns} from probabilistic properties to find a \emph{computationally-efficient} solution
	\begin{itemize}
		\item Since the origin and direction of each measurement ray is known deterministically, the set of grid cells that the ray intersects is \emph{known through geometry}
		\item A depth reading follows the forward sensor model, which \emph{only depends} on the first occupied grid cell along the measurement ray
	\end{itemize}
\end{itemize}

\begin{figure}[!htbp]
\vspace*{-0.25cm}
\centerline{
	\includegraphics[width=4.0cm]{rkplus_1.png}\hspace*{-0.5cm}
	\includegraphics[width=4.0cm]{rkplus_2.png}}
 \centerline{
	\includegraphics[width=4.0cm]{rkplus_3.png}\hspace*{-0.5cm}
	\includegraphics[width=4.0cm]{rkplus_4.png}}
\end{figure}

\begin{frame}
\frametitle{Single Measurement Ray}
\begin{itemize}
    \item Reduced Map
	\begin{itemize}
		\item Consider a reduced map of the $l$-th measurement ray, namely $r_l=\braces{\mathbf{r}_{l,1},\mathbf{r}_{l,2},\ldots,\mathbf{r}_{l,n_{r,l}}}$, consisting of grid cells \emph{intersected} by the measurement ray within the sensor limits, \emph{indexed by increasing distance}
		\item Since reduced map $r_l$ is composed of binary random variables, it has \emph{$2^{n_{r,l}}$} possible solutions
		\item However, the combinations of possible maps are grouped based on the \emph{closest occupied cells}
		\item Probability calculations have several repeated terms, and may be determined \emph{recursively}
		\item The number of possible map combinations is just \emph{$n_{r,l}+1$}
%		\item If $\mathbf{r}_{l,1}$ is occupied (a priori probability $P(\mathbf{r}_{l,1}|X_{1:t-1},Z_{1:t-1})$), then each occupancy $\mathbf{r}_{l,2:n_{r,l}}$ does \emph{not} affect forward sensor model $P(z_{t,l}|\mathbf{r}_{l,1},X_t)$
%		\item Similarly, if $\mathbf{r}_{l,2}$ is occupied (a priori probability $P(\bar{\mathbf{r}}_{l,1}|X_{1:t-1},Z_{1:t-1})P(\mathbf{r}_{l,2}|X_{1:t-1},Z_{1:t-1})$), then forward sensor model $P(z_{t,l}|\mathbf{r}_{l,2},X_t)$ is independent of grid cells of higher index
%		\item This concept is extended for all grid cells in $r_l$
	\end{itemize}
\end{itemize}
\end{frame}

%\begin{frame}
%\frametitle{Single Measurement Ray}
%\begin{itemize}
%	\item Let $P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})=\eta_{t,l}\tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})$
%	\item The $k$-th unnormalized probability is written generally as
%	{\tiny
%	\begin{align*}
%		& \tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})\\\nonumber&\quad=P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1})\nonumber\\&\quad\qquad\times 
%		\bigg[\sum_{i=1}^{k-1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]\nonumber\\
%		&\quad\quad +\qquad\quad \ \ \bigg\{\prod_{j=0}^{k-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\} p(z_{t,l}|\mathbf{r}_{l,k+},X_t)P(\mathbf{r}_{l,k}|X_{1:t-1},Z_{1:t-1})
%	\end{align*}
%	}
%	\pause
%	\item The \emph{normalizer} $\eta_{t,l}$ is
%	{\tiny
%	\begin{align*}
%		\eta_{t,l}=
%		\bigg[\sum_{i=1}^{n_{r,l}+1}\bigg\{\prod_{j=0}^{i-1}P(\bar{\mathbf{r}}_{l,j}|X_{1:t-1},Z_{1:t-1})\bigg\}p(z_{t,l}|\mathbf{r}_{l,i+},X_t)P(\mathbf{r}_{l,i}|X_{1:t-1},Z_{1:t-1})\bigg]^{-1}
%	\end{align*}
%	}
%\end{itemize}
%\end{frame}

\begin{frame}
\frametitle{Practical Implications}

\begin{itemize}
	\item Computational Efficiency
	\begin{itemize}
%		\item Several of the terms required for $\eta_{t,l}$ and $\tilde P(\mathbf{r}_{l,k}|z_{t,l},X_{1:t},Z_{1:t-1})$ for each $k=1,2,\ldots,n_{r,l}$ are repeated and need not be computed more than once
		\item \emph{Computational order $\mathcal O(n_{r,l}+1)$} for all grid cells in reduced map $r$: each grid cell once and the empty map case
		\item It is commonly believed that the computational order is $\mathcal O(2^{n_{r,l}})$; the proposed method is \emph{$2^{n_{r,l}}\left(\frac{n_{r,l}}{n_{r,l}+1}\right)$ times faster} for the \emph{same solution}
		\item Proposed method completely avoids inaccuracies associated with heuristic solutions, learned methods, and log-odds ratio update assumptions
%		\item Analytic solution is valid for any forward sensor model dependent on the closest occupied space
	\end{itemize}
	\item A \emph{ray-by-ray} approach accounts for all measurements rays composing a measurement \emph{scan}
		\begin{align*}
			P(m|X_{1:t}&,Z_{1:t})=P((\dots(((m|X_{1:t},Z_{1:t-1})|z_{t,1})|z_{t,2})|\ldots)|z_{t,n_z})
		\end{align*}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Numerical Example}

\begin{minipage}[t]{5.0cm}
\vspace*{0.5cm}
\begin{itemize}
	\item A standard \emph{approximate} inverse sensor model technique is compared with the proposed \emph{exact} method
\end{itemize}
\end{minipage}
\begin{minipage}[t]{5.0cm}
%\vspace*{0.5cm}
\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_inf_19.pdf}
        \caption*{Approximate}
    \end{subfigure}
    \hspace*{-0.1\textwidth}
    \begin{subfigure}{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_inf_19.pdf}
        \caption*{Exact}
    \end{subfigure}
\end{figure}
\end{minipage}

%\begin{figure}[!ht]
%    \centering
%    \begin{subfigure}[t]{0.35\columnwidth}
%        \centering
%        \includegraphics[width=0.5\textwidth]{AISM_Image_inf_19.pdf}
%        \caption*{Approximate}
%    \end{subfigure}
%    \hspace*{0.5cm}
%    \begin{subfigure}[t]{0.35\columnwidth}
%        \centering
%        \includegraphics[width=0.5\textwidth]{EISM_Image_inf_19.pdf}
%        \caption*{Exact}
%    \end{subfigure}
%\end{figure}

\begin{itemize}
\item The exact algorithm yields a more \emph{certain} map from the same measurement set
\end{itemize}

\section*{}

\begin{frame}
\frametitle{}
%\center
\center{\bf \color{blue} Single-Robot Autonomous Exploration}
\end{frame}

\subsection*{Single-Robot Autonomous Exploration}

\begin{frame}
\frametitle{Introduction}
\begin{itemize}
        	\item The environment is initially uncertain, so the robot path is initially unknown
	\item Simultaneous localization and mapping assumes robotic actions are provided
	\item Human interaction is common to guide the robot
	\item Goal: develop effective policies to govern robotic motion 
\end{itemize}

\begin{frame}
\frametitle{Problem Definition}
\begin{itemize}
        	\item Uncertainty-Based Exploration
	\begin{itemize}
		\item Main idea: choose robot motions that minimize the uncertainty of the occupancy grid map
		\item Equivalently maximize map information gain
	\end{itemize}
\end{itemize}
\begin{minipage}[t]{7.0cm}
\begin{itemize}
	\item Entropy
	\begin{itemize}		
		\item \emph{Shannon's entropy} serves as an uncertainty measure
		\begin{align*}
			H(P)=-P\log P-\bar{P}\log \bar{P}%-(1-P)\log(1-P)
		\end{align*}
		with cell occupancy probability $P$ and complement $\bar{P}=1-P$
		\item Entropy $H$ is maximized when $P=0.5$ and minimized as $P\rightarrow0$ or $P\rightarrow1$
	\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[t]{3.0cm}
\vspace*{0.5cm}
\begin{figure}[!htbp]
	\centerline{
		\hspace*{1.25cm}
   		\includegraphics[width=5.0cm]{H_Plotted_square.pdf}%\hspace*{0.1cm}
	}
\end{figure}
\end{minipage}

@@

\begin{frame}
\frametitle{Related Work}
\begin{itemize}
        	\item Frontier-Based Exploration
	\begin{itemize}
		\item Main idea: robot moves toward boundaries between certain and uncertain space, takes measurements, then pushes back the boundaries
		\item Non-entropy-based exploration
		\item Heuristic
	\end{itemize}
	\pause
	\item Entropy-Based Exploration
	\begin{itemize}
		\item Cell occupancy probabilities are inaccurate: inverse sensor model is heuristic or learned, and frequently estimated with Rao-Blackwellized particle filters
		\item Inaccurate probabilities imply inaccurate entropy measures
		\item Approaches use ``hallucination measurements'' to predict how future measurements \emph{might} affect the map uncertainty,
		\begin{align*}
			\text{E}\left[H(P(m|X_{1:t},Z_{1:t},X_c,Z_c))\right]\approx H(P(m|X_{1:t},Z_{1:t},X_c,\text{E}\left[Z_c\right]))
		\end{align*}
	\end{itemize}
\end{itemize}

@@

\begin{frame}
\frametitle{Direct Entropy Calculation}
\begin{itemize}
        	\item Instead of relying on frontiers or making assumptions about measurements, the expected map entropy is \emph{calculated directly} by the law of total expectation:
	\begin{align*}
		\text{E}[H(P(m|X,z))]=\int_{z_\text{min}}^{z_\text{max}}
		H(P(m|X,z))p(z|X)dz,
	\end{align*}
	\item The robot pose is chosen to maximize map information gain from this expectation
	\item Dijkstra's algorithm provides collision-free waypoints for the robot path
	\item Smooth trajectory: constrained polynomial least squares 
\end{itemize}

@@

\begin{frame}
\frametitle{Numerical Results}
	\centering{
	\includemovie[poster,autoplay]{0.720\textwidth}{0.576\textwidth}{JIRS16_simulation_speedup10x_then_speedup100x.mov}}
\end{frame}

@@

\begin{frame}
\frametitle{Experimental Results}
	\centering{
	\includemovie[poster,autoplay]{0.720\textwidth}{0.576\textwidth}{JIRS16_experiment_SideBySide_speedup8x.mov}}
\end{frame}
